Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches

### 2017-10-19 paper.tex
plots

\begin{figure}[H]
  \includegraphics{paperDiagram.png}
  \caption{The three steps of the G-PTM-D workflow are indicated in the light beige color.}
  \label{fgr:diagram}
\end{figure}

@@

This work presents four major changes to the previously published G-PTM-D workflow:
a spectral calibration;
a replacement of the open search with a custom multi-notch search for PTM discovery;
replacement of the final traditional narrow mass search with a limited multi-notch search that permits identification of incorrectly deconvoluted precursor masses;
and lastly, addition of capacity for identification of multiple co-fragmented peptides from a single MS/MS scan.
To clarify the advantage of each change, they are first discussed separately, followed by an analysis of their combined effect upon overall G-PTM-D performance.

>>>>

\begin{figure}[H]
  \includegraphics[scale=0.1]{paperDiagram.png}
  \caption{The three steps of the G-PTM-D workflow are indicated in the light beige color.}
  \label{fgr:diagram}
\end{figure}

@@

This work presents four major changes to the previously published G-PTM-D workflow:
a spectral calibration;
a replacement of the open search with a custom multi-notch search for PTM discovery;
replacement of the final traditional narrow mass search with a limited multi-notch search that permits exact matches even when incorrectly deisotoped precursor masses are present;
and lastly, addition of capacity for identification of multiple co-fragmented peptides from a single MS/MS scan.
To clarify the advantage of each change, they are first discussed separately, followed by an analysis of their combined effect upon overall G-PTM-D performance.
